Pilot data analysis

### 2021-03-27 data_analysis_brms_updated.Rmd
Method section (beginning)

```{r lmm1}
contrasts(exp1_data_to_include$Condition) <- c(-1,1)
contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

@@

lmm_exp2 <- lmer(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

@@

blmm_exp2 <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt < 1500), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

                 #blmm_exp1_full <- update(blmm_exp1,
#                         warmup = 1000,
#                         iter = 5000, 
#                         chains = 4,
#                         prior = prior_exp1,
#                         family = exgaussian(),
#                         inits = "random",
#                         control = list(adapt_delta = 0.95),
#                         cores = 4, 
#                         backend = "cmdstanr", 
#                         threads = threading(2))

save(blmm_exp2, file = "blmm_exp2.RData")
```

>>>>

```{r lmm1}
contrasts(exp1_data_to_include$Condition) <- c(-1,1)
contrasts(exp1_data_to_include$PrimeDuration) <- c(-1,1)
lmm_exp1 <- lmer(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

@@

lmm_exp2 <- lmer(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), rt ~ Condition * PrimeDuration + (1|source) + (1|Target))

@@

blmm_exp1_rt <- brm(data = exp1_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

save(blmm_exp1_rt, file = "blmm_exp1_rt_new.RData")

blmm_exp1_acc <- brm(data = exp1_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                 warmup = 1000,
                 iter = 5000,
                 chains = 4,
                 prior = prior_exp1,
                 family = bernoulli(link = "logit"),
                 inits = "random",
                 control = list(adapt_delta = 0.95),
                 cores = 4, backend = "cmdstanr", threads = threading(2))

save(blmm_exp1_acc, file = "blmm_exp1_acc_new.RData")

### Experiment 2

blmm_exp2_rt <- brm(data = exp2_data_to_include %>% filter(corr == 1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
                        rt ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                        warmup = 1000,
                        iter = 5000,
                        chains = 4,
                        prior = prior_exp1,
                        family = exgaussian(),
                        inits = "random",
                        control = list(adapt_delta = 0.95),
                        cores = 4, backend = "cmdstanr", threads = threading(2))

save(blmm_exp2_rt, file = "blmm_exp2_rt_new.RData")

blmm_exp2_acc <- brm(data = exp2_data_to_include %>% filter(corr != -1 & StimulusType == "WORD" & rt > 250 & rt < 2000), 
                 formula = corr ~ Condition * PrimeDuration + (1 + Condition * PrimeDuration|source) + (1 + Condition * PrimeDuration|Target),
                 warmup = 1000,
                 iter = 5000,
                 chains = 4,
                 prior = prior_exp1,
                 family = bernoulli(link = "logit"),
                 inits = "random",
                 control = list(adapt_delta = 0.95),
                 cores = 4, backend = "cmdstanr", threads = threading(2))

save(blmm_exp2_acc, file = "blmm_exp2_acc_new.RData")
